ERSPAN Support for Linux

### 2018-11-05 paper.tex
fix tc use cases

# creating erspan dev named "myerspan" and attach
ip link add dev myerspan type erspan external
ovs-dpctl add-if mydp myerspan

# flow entry for port 2 to erspan tunnel 
ovs-dpctl add-flow \
    "in_port(2)" \
    "set(tunnel(tun_id=20,dst=192.168.1.1,ttl=64,\
    erspan(ver=2,dir=1,hwid=0x4),flags(df|key))),3"
\end{verbatim}
}
%\begin{lstlisting}
%[caption={Example ovs-dpctl usage},language=bash,label=lst:dpctl,breaklines=true]
%\end{lstlisting}

@@

{\footnotesize
\begin{verbatim}
# Native-mode without using eBPF
ip link add dev myerspan type erspan seq key 30 \
    local 192.168.1.4 remote 192.168.1.1 \
    erspan_ver 1 erspan 123
tc filter add dev eth1 ingress pref 1000 matchall \
    skip_hw action mirred egress mirror dev myerspan

# Metadata-mode with eBPF
ip link add dev myerspan type erspan external
tc qdisc add dev myerspan clsact
tc filter add dev myerspan egress bpf direct-action \
    obj test_tunnel_kern.o section erspan_set_tunnel
tc filter add dev eth1 ingress pref 1000 matchall \
    skip_hw action mirred egress mirror dev myerspan
\end{verbatim}
}
Note that for metadata-mode tunnel, the tunnel configuration is not
provided from the ip route command line, but is passed in to the tunnel
by the eBPF program, test\_tunnel\_kern.o. A code snippet creating this
object from tools/testing/selftests/bpf/test\_tunnel\_kern.c is shown below.
{\footnotesize
\begin{verbatim}
SEC("erspan_set_tunnel")
int _erspan_set_tunnel(struct __sk_buff *skb)
{
    struct bpf_tunnel_key key;
    struct erspan_metadata md; 
    int ret;

>>>>

# creating erspan dev named "myerspan" and attach
# lightweight tunnel is used with "external" keyword
ip link add dev myerspan type erspan external
ovs-dpctl add-if mydp myerspan

# flow entry for port 1 to erspan tunnel port 3 
ovs-dpctl add-flow \
  "in_port(1),eth(src=00:01:02:03:04:05,dst=10:11:12:13:14:15),\
  eth_type(0x0800),ipv4(src=35.8.2.41,dst=172.16.0.20,proto=5,\
  tos=0x80,ttl=128,frag=no)" \
  "set(tunnel(tun_id=20,dst=192.168.1.1,ttl=64,\
  erspan(ver=2,dir=1,hwid=0x4),flags(df|key))),3"

ovs-dpctl dump-flows
\end{verbatim}
}
%\begin{lstlisting}
%[caption={Example ovs-dpctl usage},language=bash,label=lst:dpctl,breaklines=true]
%\end{lstlisting}

@@

{\footnotesize
\begin{verbatim}
# Native-mode without using eBPF
ip link add dev myerspan type erspan seq key 30 \
    local 192.168.1.4 remote 192.168.1.1 \
    erspan_ver 1 erspan 123

# eth1 is the mirrored device
tc qdisc add dev eth1 handle ffff: ingress
tc filter add dev eth1 handle ffff: ingress matchall \
    skip_hw action mirred egress mirror dev myerspan

# Metadata-mode with eBPF
ip link add dev myerspan type erspan external
tc qdisc add dev myerspan clsact
tc filter add dev myerspan egress bpf direct-action \
    obj test_tunnel_kern.o section erspan_set_tunnel

tc qdisc add dev eth1 handle ffff: ingress
tc filter add dev eth1 parent ffff: matchall \
    skip_hw action mirred egress mirror dev myerspan
\end{verbatim}
}
Note that for metadata-mode tunnel, the tunnel configuration is not
provided from the ip route command line, but is passed in to the tunnel
by the eBPF program, test\_tunnel\_kern.o. A code snippet creating this
object from tools/testing/selftests/bpf/test\_tunnel\_kern.c is shown below.
{\footnotesize
\begin{verbatim}
SEC("erspan_set_tunnel")
int _erspan_set_tunnel(struct __sk_buff *skb)
{
    struct bpf_tunnel_key key;
    struct erspan_metadata md; 
    int ret;
